PLANETESIMAL ACCRETION AT SHORT ORBITAL PERIODS

### 2021-11-28 main.tex
Add text discussing full disk sims

\begin{table}
\begin{center}
\caption{Summary of Full Disk Simulations Run}
\begin{tabular}{lllll} \hline \hline
Name     & A & $\alpha$ &  &  \\ \hline
fdHi                 & 100                                                         & 1.5                              &  &  \\
fdHiShallow     & 100                                                        & 0.5                              &  &  \\
fdHiSteep       & 100                                                         & 2.5                              &  &  \\
fdLo                & 1                                                             & 1.5                              &  &  \\ \hline
\end{tabular}
\label{tab:sims}
\end{center}
\end{table}

@@

>>>>

\begin{table}
\caption{Summary of Full Disk Simulations Run}
\begin{tabular}{llllll} \hline \hline
Name    & $m_{pl}^{a}$ & $N_{pl}^{b}$ & $A^{c}$ & $\alpha^{d}$ &  \\ \hline
fdHi                 & $5 \times 10^{22}$ & 903,687 & 100                                                         & 1.5                              &   \\
fdHiShallow    & $5 \times 10^{22}$ & 903,687 & 100                                                        & 0.5                              &   \\
fdHiSteep       & $5 \times 10^{22}$ & 903,687 & 100                                                         & 2.5                              &   \\
fdLo                & $1 \times 10^{22}$ & 45,185    & 1                                                             & 1.5                              &   \\ \hline
\end{tabular}
\begin{flushleft}
\textsc{Note} \\ {$^a$ Planetesimal mass [g] \\
		       $^b$ Number of planetesimals \\
		       $^c$ Solid surface density normalization (relative to MMSN) \\
		       $^d$ Solid surface density power law index } \\
\end{flushleft}
\label{tab:sims}
\end{table}

@@

\subsection{Results}

\begin{table}
\caption{Final Properties of Full Disk Simulations}
\begin{tabular}{lllll} \hline \hline
Name     & $M_{PP}^a$ & $T_{int}^b$ & $T_{int 1}^c$ &  \\ \hline
fdHi                 & 100                                                         & 1.5                              & 4  &  \\
fdHiShallow     & 100                                                        & 0.5                              & 4  &  \\
fdHiSteep       & 100                                                         & 2.5                              & 4 &  \\
fdLo                & 1                                                             & 1.5                              & 4 &  \\ \hline
\end{tabular}
\label{tab:sim_properties}
\begin{flushleft}
\textsc{Note} \\ {$^a$ Maximum protoplanet mass [$M_{earth}$] \\
		       $^b$ Integration time [yr] \\
		       $^c$ Rescaled integration time [yr]} \\
\end{flushleft}
\end{table}

In all four simulations, the timescales for embryo formation depend on the chosen surface density profile, along with the particular location in the disk. Protoplanets form first near the inner edge of the disk, where the dynamical timescales are short. Growth proceeds in an inside-out fashion, with the outermost regions of the disk completing the protoplanet assembly phase last. This fact is not typically accounted for in planet formation simulations, and appears to be an important component to forming realistic solar system analogs \citep{clement20}. As with the narrow annulus simulations, we stop the integration once the mass of protoplanets in the outermost region of the disk reach a steady value. In table \ref{tab:sim_properties}, we summarize the outcomes of the four `full disk' cases.

We show the final state of the `fiHi' simulation in figure \ref{fig:fulldisk_e_m}. In the top panel, the initial (contours) and final (points) state of the simulation is shown in orbital period and eccentricity. The size of the points indicates the relative mass of the bodies. In the bottom panel, the mass of the largest bodies is shown as a function of orbital period. The solid curves indicate the isolation mass

\begin{equation}\label{eq:iso}
	M_{iso} = \left[ \frac{\left( 2 \pi a^2 \Sigma \tilde{b} \right)^3}{3 M_{*}} \right]^{1/2},
\end{equation}

\noindent where $\tilde{b}$ is the size of the feeding zone in units of Hill radii. For a body on a circular orbit $\tilde{b} = 2 \sqrt{3}$, while a protoplanet formed by oligarchic growth typically has $\tilde{b} = 10$ \citep{kokubo98}. The isolation mass is plotted in blue and orange for these two values of $\tilde{b}$, respectively.

A qualitative shift in the protoplanet and planetesimal distribution is visible at $\sim$ 60 days. Interior to this location, there are very few remaining planetesimals and the embryos formed are noticeably more massive. Protoplanets in this region appear to closely follow the isolation mass curve for $\tilde{b} = 10$. Exterior to the boundary, the residual planetesimal population is much more numerous, and protoplanets more closely follow the $\tilde{b} = 2 \sqrt{3}$ curve. This tentatively suggests that the transition between the low $\alpha$ and high $\alpha$ accretion modes seen in section \ref{sec:narrow} happens near this location.

In figure \ref{fig:alpha_pl_frac}, we show $\alpha$ (left axis) and the fraction of remaining planetesimals (right axis) as a function of orbital period. Here, the fraction of remaining planetesimals is measured by dividing the disk into 15 semimajor axis bins and using the profile function in {\sc pynbody} to measure the total solid surface density $\Sigma$ in each of those bins, and also the planetesimal surface density $\sigma$. Here, a planetesimal is defined to any body with $m < 10 m_{pl}$. Exterior to 60 days in orbital period, $\sigma/\Sigma$ sharply increases, indicating that the highly efficient accretion mode seen previously does not operate here. As can be seen from the plot, the accretion boundary roughly corresponds to $\alpha = 0.1$.
